Deep Reinforcement Learning for Conservation Decisions

### 2021-06-09 manuscript/manuscript.Rmd

Over the course of training, RL agents will engage in trial and error learning, whereby it will be necessary for the agent to explore new sequences of actions as well as exploit past high rewarding sequences.
Occasionally, the agent will need to propose exploratory actions that may result in higher rewards than previously seen. 
The agent may also need to focus on past sequences of actions which may require marginal improvement to reach optimality.
It is very difficult for the agent to know when it should engage in explorative or exploitative behavior. 
This *exploration-exploitation dilemma* is an open research problem [@berger-tal_exploration-exploitation_2014]. 
Current deep RL algorithms take a range of approaches towards this (see  Appendix A).
The manner in which RL algorithms explore depend on whether the algorithms are *on-policy* or *off-policy*.
The distinction between on and off-policy evaluation comes from what policy the agent is using to select actions during training.
For off-policy algorithms, the agent uses a policy during training that can be different from the policy that the agent will use during evaluation; while in on-policy algorithms, the agent updates the same policy in training as the agent will use during evaluation.
Other points of divergence include whether the agent learns a deterministic or stochastic policy, and
whether the algorithm is formulated to work on a discrete, continuous or both a discrete and continuous state and action space.

>>>>

On top of these distinctions of deep RL algorithms, there are other algorithms design choices to be made. 
A significant consideration is deciding how the agent will explore the environment.
Another is whether the algorithm can work on a discrete, or continuous state and action space.
In Appendix A, we provide more detail on the important components of RL algorithms.
